fGFPCA dynamic prediction

### 2023-03-07 f-GFPCA.Rmd
start manuscript

```{r, fig.width=8, fig.height=4}
# compare point prediction with in-sample
# subject 1
grid.arrange(
  out_pred_subj1 %>% 
    group_by("type") %>%
    ggplot()+
    geom_line(aes(x=mid, y=true), col = "black")+
    geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
              show.legend = FALSE)+
    labs(x="Binned time", title = "Subject 1 out-of-sample prediction"),

>>>>

```{r, fig.width=6, fig.height=3}
# compare point prediction with in-sample
# subject 1
grid.arrange(
  out_pred_subj1 %>% 
    group_by("type") %>%
    ggplot()+
    geom_line(aes(x=mid, y=true), col = "black")+
    geom_line(aes(x=mid, y=eta, col= type, group = type), linetype="dashed", na.rm = T,
              show.legend = FALSE)+
    labs(x="Binned time", title = "Subject 1 out-of-sample prediction"),
